\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
[wip] conclusion

We demonstrated that eye-tracking data can provide several process
variables to assess not only the task-based performance of the
participants but also to analyse HRI situations.

The advantages of mobile eye-tracking come with an additional cost. As
we mentioned earlier, the automatic localisation of the gaze pointer on
the visual stimulus is not a trivial task. To do this we have to use a
number of fiducial markers to the playground (Figure 2). We observed
that the fiducial markers cause a distraction to the participants. As a
future work, we are trying to find a suitable replacement to the
fiducial markers.

Our effort to use the confluent of eye tracking and human-robot
interaction provides insights to two aspects: first, as a way to
evaluate the human-robot interaction and second, as a way to evaluate
the interaction scenario.

%We addressed two research questions in the beginning of the present
%work. The results show that the way the sensor data is visualised has an
%impact on both the gaze patterns and the performance (Question 2).
%However, for the relation between the gaze patterns of the participants
%and their performance outcomes (Question 1) we cannot claim a direct
%relation. We found a negative correlation between the gaze-patterns and
%the first improvement during the interaction phase. We could not find a
%relation between the explanation of the participants and their
%gaze-patterns. Moreover, we did not find any anticipation patterns in
%the gaze data. The lack of evidence for the relation between
%participants' explanations and their gaze patterns prevents us to make
%any strong claims about the relation between the overall performance and
%the gaze patterns.
%
%The fact that we cannot find a relation between the gaze patterns and
%all the factors in the performance might have its roots in the way we
%designed the interaction phase experiment. As a working hypothesis we
%said that there should be clear and carefully designed mapping between
%the robots' behaviour and the sensor data visualization. Its environment
%also affects the behaviour of the robot and hence the environment also
%should be taken into consideration while designing the
%behavior-visualisation mapping. We introduced a novelty (the gray
%obstacle being more reflective) in the environment during the
%interaction phase of the experiment that forced the participants to
%revise their hypothesis and hence they failed to understand the robot's
%functionality. This also serves as a word of caution in future while
%designing such interactions. The observation phase serves as a training
%session for the participants, which can later be tested during the
%interaction phase. Any novel behaviour modality (in our case, the more
%reflective grey obstacle) can have a negative impact on the
%participants' understanding.

>>>>

The task that we have presented was initially motivated by those two questions:

\begin{enumerate}
    \item Can we characterise the participants' behaviours that
        lead to good performance during the interaction? In particular, do
        we observe any anticipation patterns for the good performers?

    \item How does visual cue affects the performance of the participants?

\end{enumerate}

The task was performance-oriented and yet we were interested in accessing and
understanding the cognitive mechanisms at stake during the interaction: where do
the participant look when they want to understand a robot behaviour? does
\emph{anticipation} reflect understanding? how the robot's design impact the
interaction?

We believe that mobile eye-tracking, as a relatively non-invasive yet accurate
(both spatially and temporally) biometric measurement, is a key tool to
investigate this kind of questions in ecologically valid environments.

One need to be aware of its limitations: eye-tracking does not give a direct
access to underlying mental representations, and a gaze pattern does not
automatically tell us what the subject think of (EEG or fMRI may be slightly
closer to that target, but they come with their own range of limitations).

Besides, mobile eye-tracking come with an additional cost. As
we mentioned earlier, the automatic localisation of the gaze pointer on
the visual stimulus is not a trivial task. In our study, we relied on a 
number of fiducial markers to the playground, but they were reported as
distractive by the participants. More complex computer vision tools (object
tracking) can alleviate the need for such markers, but it certainly requires
significant pre-processing prior to data analysis.

The results show that the way the sensor data is visualised has an
impact on both the gaze patterns and the performance (Question 2).
However, for the relation between the gaze patterns of the participants
and their performance outcomes (Question 1) we cannot claim a direct
relation. We found a negative correlation between the gaze-patterns and
the first improvement during the interaction phase. We could not find a
relation between the explanation of the participants and their
gaze-patterns. Moreover, we did not find any anticipation patterns in
the gaze data. The lack of evidence for the relation between
participants' explanations and their gaze patterns prevents us to make
any strong claims about the relation between the overall performance and
the gaze patterns.

%
%The fact that we cannot find a relation between the gaze patterns and
%all the factors in the performance might have its roots in the way we
%designed the interaction phase experiment. As a working hypothesis we
%said that there should be clear and carefully designed mapping between
%the robots' behaviour and the sensor data visualization. Its environment
%also affects the behaviour of the robot and hence the environment also
%should be taken into consideration while designing the
%behavior-visualisation mapping. We introduced a novelty (the gray
%obstacle being more reflective) in the environment during the
%interaction phase of the experiment that forced the participants to
%revise their hypothesis and hence they failed to understand the robot's
%functionality. This also serves as a word of caution in future while
%designing such interactions. The observation phase serves as a training
%session for the participants, which can later be tested during the
%interaction phase. Any novel behaviour modality (in our case, the more
%reflective grey obstacle) can have a negative impact on the
%participants' understanding.
